Preliminary Draft

### 2021-07-26 article/draft.tex
some typos in the discussion section

\tableofcontents

@@

Finally, we are aware that full transparency regarding operational aspects of misinformation related interventions can backfire. This is because, the prospective aimed users might find means to circumvent the partly automated interventions. To provide an example, it is very likely that YouTube is allocating an information panel on all YouTube videos mentioning COVID-19 and related terms in their title (see section \ref{youtube_panels}). Yet, we noticed during the present study, that some YouTube channels are trying to avoid the likely automated information panels, by using notational variants such as ``C.O.V.I.D'' or ``C O V I D''. Similarly, we came across  notational variants on Twitter of domain names with several failed fact-checks. To provide an example, Twitter users introduce  the following notational variants when sharing an article from the website\footnote{Here is an example of a failed fact-check of one of the articles of the website {\it off-guardian.org} : \href{https://www.politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}{politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}} {\it off-guardian.org}: {\it off-guardian. org}, {\it off-guardian .org}, {\it off-guardian./org}, {\it off-guardian*org}. For the case of this domain name, we successfully managed to post a Tweet containing the domain name {\it off-guardian.org}, which we deleted after a few seconds. In other words, users can include in their Tweets links containing  {\it off-guardian.org} and only a warning message appears when a user clicks on the link. For this case, we failed to understand precisely what kind of intervention the users were circumventing. Hence, a balance is needed between: $(i)$ fully transparent communication about misinformation related interventions so that the users can understand how the platforms are regulating their content, and $(ii)$ not explicitly giving too much information which would allow the policies to be bypassed.

@@

{\bf Scattered data.} Third, to study online misinformation, researchers, NGOs and data journalists turn to multiple APIs besides the official ones managed by the mainstream platforms themselves (e.g. BuzzSumo). They do so, because multiple data sources can be complementary and no specific API has complete data. {\color{red} [to be drafted by HT... and cite the article ~\cite{api} about APIs].}

>>>>

{\color{pink} \noindent N.B: we will redo all the figures (to harmonize the legend, etc.) and the table of contents will be deleted.} 
\tableofcontents

@@

We are aware that full transparency regarding operational aspects of misinformation related interventions can backfire. This is because, the prospective aimed users might find means to circumvent the partly automated interventions. To provide an example, it is very likely that YouTube is allocating an information panel on all YouTube videos mentioning COVID-19 and related terms in their title (see section \ref{youtube_panels}). Yet, we noticed during the present study, that some YouTube channels are trying to avoid the likely automated information panels, by using notational variants such as ``C.O.V.I.D'' or ``C O V I D''. Similarly, we came across  notational variants on Twitter of domain names with several failed fact-checks. To provide an example, Twitter users introduce  the following notational variants when sharing an article from the website\footnote{Here is an example of a failed fact-check of one of the articles of the website {\it off-guardian.org} : \href{https://www.politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}{politifact.com/factchecks/2020/jul/07/blog-posting/covid-19-tests-are-not-scientifically-meaningless/}} {\it off-guardian.org}: {\it off-guardian. org}, {\it off-guardian .org}, {\it off-guardian./org}, {\it off-guardian*org}. For the case of this domain name, we successfully managed to post a Tweet containing the domain name {\it off-guardian.org}, which we deleted after a few seconds. In other words, users can include in their Tweets links containing  {\it off-guardian.org} and only a warning message appears when a user clicks on the link. For this case, we failed to understand precisely what kind of intervention the users were circumventing. Hence, a balance is needed between: $(i)$ fully transparent communication about misinformation related interventions so that the users can understand how the platforms are regulating their content, and $(ii)$ not explicitly giving too much information which would allow the policies to be bypassed.

@@

{\bf Scattered data.} Third, to study online misinformation, researchers, NGOs and data journalists turn to multiple APIs besides the official ones managed by the mainstream platforms themselves (e.g. BuzzSumo). They do so, because multiple data sources can be complementary and no specific API has complete data. {\color{red} [to be drafted by HT... and cite the article ~\cite{api} about APIs]....} we found irregularities in the number of Infowars articles collected from Buzzsumo. While Infowars usually publishes $20$ to $30$ articles per day, only $53$ articles were collected in the $31$-day period between June $11$ to July $11$, 2020. A temporary crawling problem coming from Buzzsumo may have caused this lack of data. Because no database is perfect, we would like to highlight the importance of cross-checking information between different sources when possible.
